---
title: "COVID-19 In Japan"
description: |
  Welcome to our new blog, In this blog, we explore the different impact of COVID has resulted in Japan We hope you enjoy reading what we have to say!
author:
  - name: Qin Xu 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: 08-31-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE)
```

```{r}
library(here)
```

## Introduction
Covid- 19 is a disease caused by a form of coronavirus that can cause respiratory infections that can range from the common cold to more serious diseases.With its strong trasnmissiblity among public, it is true indeed to say that the COVID-19 pandemic has presented an unprecedent challenge to public health across the globe with a continue increase in the number of the people confirmed with the virus. Thus, to better understand the virus and its characteristic, we will be examining the the impact COVID-19 pandemic in Japan.


## Data description

To conduct our exploration of the impact of COVID in japan, we will be using multiple datasets (this includes number of death from COVID-19, number of recovery from COVID-19, Number of people who have taken the PCR test, Number of positive cases) for our analysis.
All the datasets were sourced from Toyo Keizai Online "Coronavirus Disease (COVID-19) Situation Report in Japan" with its orginal data provided by the Ministry of Health, Labor and Welfare in Japan, and the other dataset are provided by our world in data with its orginal data sourced from COVID-19 Data Repository by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University (JHU)

```{r results = FALSE }
death_data <- read.csv(here::here("data/death_total.csv"))

recovery_data <- read.csv(here::here("data/recovery_total.csv"))

pcr_postive_daily_data <- read.csv(here::here("data/pcr_positive_daily.csv"))

pcr_tested_daily_data <- read.csv(here::here("data/pcr_positive_daily.csv"))

```




